Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-22 paper/paper.Rmd
discussion tweaks

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relativley close replications and included the same or greater numbers of participants. Yet, despite these virtues, our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate of replication?

>>>>

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants. Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects.

Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate of replication?
